|

### 2021-02-25 manuscript/article.Rmd
add ethics statement, small edits

We pre-registered the experiment on the Evidence in Governance and Policy
(EGAP) website (<https://osf.io/6q8vu/>), and received IRB approval from New
York University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). The
funders of this study had no influence over the formulation, organisation,
analysis, and interpretation of the outcomes. Healthcare workers gave written
consent upon filling the Qualtrics questionnaire. During the intervention, the
occupants of households inspected for breeding sites and larvae gave oral
consent. For more information on the experimental design, sample
characteristics, exclusion criteria, and estimation methods, please refer to
the Supplementary Material.

>>>>

## Ethics Statement

We pre-registered the experiment on the Evidence in Governance and Policy
(EGAP) website (#20180504AA, <https://osf.io/6q8vu/>), and received IRB
approval from New York University (IRB-FY2017-17) and Fundação Getulio Vargas
(IRB-01/2017). The funders of this study had no influence over the formulation,
organisation, analysis, and interpretation of the outcomes. Healthcare workers
gave written consent upon filling the pre-treatment questionnaire. During the
intervention, the occupants of households inspected for breeding sites and
larvae gave verbal consent. For more information about the experimental design, please refer to the Supplementary Material.
